---
title: "Survey Data Report"
author: "Kenna Reagan"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---

```{r include=FALSE}
# load libraries
library(gsheet) # to load data from the google sheet
library(tidyverse)
library(dplyr)
library(lubridate) # format date from chr to date
library(ggplot2) # create graphics 
library(wesanderson)

```


```{r include=FALSE}
# import data from google sheets, convert to tibble, save to a variable
url1 <- 'https://docs.google.com/spreadsheets/d/1Jwj-H3T28nySYGttAwA_9bUE_kKRR2jq/edit#gid=1872698168'
url2 <-'https://docs.google.com/spreadsheets/d/1Jwj-H3T28nySYGttAwA_9bUE_kKRR2jq/edit#gid=771323801'
survey <- gsheet2tbl(url1)
org <- gsheet2tbl(url2)

# print the tibbles 
survey
org

# check the dimensions of each tibble for comparison after joining them
dim(survey)
dim(org)
```

```{r include=FALSE}
# join org data on 'Primary Facilitator' coloumn so that we have the org data for the primary facilitator
data <- left_join(survey, org, by = c("Primary Facilitator" = "Faciliator ID")) 

# check the dimensions to make sure we didn't lose data
dim(data)
data
data$Date <- as.Date(data$Date, format = "%m/%d/%Y")

# replace null values with 0 or 'N/A'
data$`Likely to recommend Instruction Partners`[is.na(data$`Likely to recommend Instruction Partners`)]<- 0
data[is.na(data)] <- "N/A"
```

```{r include=FALSE}
# get counts of each answer, grouped by date
Q1 <- data %>% group_by(Date,`Clear about change we seek`) %>% summarise(var_counts = n())
Q2 <- data %>% group_by(Date,`Clear about roles and responsibilities`) %>% summarise(var_counts = n())
Q3 <- data %>% group_by(Date,`Confident plan will achieve goals`) %>% summarise(var_counts = n())
Q4 <- data %>% group_by(Date,`Feel more equipped`) %>% summarise(var_counts = n())
Q5 <- data %>% group_by(Date,`Equipped and supported`) %>% summarise(var_counts = n())
Q6 <- data %>% group_by(Date,`Understand state of instruction`) %>% summarise(var_counts = n())
Q7 <- data %>% group_by(Date,`Valuable use of my time:`) %>% summarise(var_counts = n())

# get monthly averages for how likely people are to recommend Instruction Partners
Q8 <- filter(data, `Likely to recommend Instruction Partners` > 0) %>%
        mutate(month = floor_date(Date, "month")) %>%
           group_by(month) %>%
           summarize(avg = mean(`Likely to recommend Instruction Partners`))
```
### Overall Performance

Overall, the performance is high, with the monthly averages remaining above 8. The highest averages align with the beginning of the school year, while the lowest averages appear during winter break.

```{r echo=FALSE, warning=FALSE}
# create time series plot 
ggplot(Q8 ,aes(x=month,y=avg)) + geom_line(color="#1D549E",size=1) + geom_point(color="#1D549E",size=2) + theme(panel.background = element_rect(fill="#F0EDED",color="#F0EDED"))+ ggtitle("Monthly 'Likely to recommend Instruction Partners' Average") +xlab("Date") + ylab("'Likely to recommend Instruction Partners' Average") 
```



```{r include=FALSE}
# remove all 0's (non-answers), sort by month, get the mean for each month
Q8 <- filter(data, `Likely to recommend Instruction Partners` > 0) %>%
  mutate(month = floor_date(Date, "month")) %>%
           group_by(month, Team) %>%
           summarize(avg = mean(`Likely to recommend Instruction Partners`))

Q8
```

## Team Performance {.tabset}
Team 8 was an outlier. They hosted one event in September and were given a rating of 2. Apart from that, Team 5 had the lowest average performance of 6 in January. However, they also had the highest average performance of 10 in December. Team performances mirrored that of the overall monthly averages.
<br />

### Team 1
```{r echo=FALSE, warning=FALSE}
# plot the monthly mean for Team 1
ggplot(Q8, aes(month, avg)) + geom_line(data=subset(Q8,Team=="Team 1"),color="#E69F00", size=1) + geom_point(data=subset(Q8,Team=="Team 1"),size=2,color="#E69F00")+ theme(panel.background = element_rect(fill="#F0EDED",color="#F0EDED")) + ggtitle("Monthly 'Likely to recommend Instruction Partners' Average") +xlab("Date") + ylab("'Likely to recommend Instruction Partners' Average") 
```

### Team 2
```{r echo=FALSE, warning=FALSE}
# plot the montly mean for Team 2
ggplot(Q8, aes(month, avg)) + geom_line(data=subset(Q8,Team=="Team 2"),size=1,color="#56B4E9") + geom_point(data=subset(Q8,Team=="Team 2"),size=2,color="#56B4E9")+ theme(panel.background = element_rect(fill="#F0EDED",color="#F0EDED")) + ggtitle("Monthly 'Likely to recommend Instruction Partners' Average") +xlab("Date") + ylab("'Likely to recommend Instruction Partners' Average") 
```

### Team 3
```{r echo=FALSE, warning=FALSE}
# plot the monthly mean for Team 3
ggplot(Q8, aes(month, avg)) + geom_line(data=subset(Q8,Team=="Team 3"),size=1,color="#009E73")+ geom_point(data=subset(Q8,Team=="Team 3"),size=2,color="#009E73")+ theme(panel.background = element_rect(fill="#F0EDED",color="#F0EDED")) + ggtitle("Monthly 'Likely to recommend Instruction Partners' Average") +xlab("Date") + ylab("'Likely to recommend Instruction Partners' Average") 
```

### Team 4
```{r echo=FALSE, warning=FALSE}
# plot the monthly mean for Team 4
ggplot(Q8, aes(month, avg)) + geom_line(data=subset(Q8,Team=="Team 4"),size=1,color="#F0E442")+ geom_point(data=subset(Q8,Team=="Team 4"),size=2,color="#F0E442")+ theme(panel.background = element_rect(fill="#F0EDED",color="#F0EDED")) + ggtitle("Monthly 'Likely to recommend Instruction Partners' Average") +xlab("Date") + ylab("'Likely to recommend Instruction Partners' Average") 
```

### Team 5
```{r echo=FALSE, warning=FALSE}
# plot the montly means for Team 5
ggplot(Q8, aes(month, avg)) + geom_line(data=subset(Q8,Team=="Team 5"),size=1,color="#0072B2")+ geom_point(data=subset(Q8,Team=="Team 5"),size=2,color="#0072B2")+ theme(panel.background = element_rect(fill="#F0EDED",color="#F0EDED")) + ggtitle("Monthly 'Likely to recommend Instruction Partners' Average") +xlab("Date") + ylab("'Likely to recommend Instruction Partners' Average") 
```


### Team 6
```{r echo=FALSE, warning=FALSE}
# plot the montly mean for Team 6
ggplot(Q8, aes(month, avg)) + geom_line(data=subset(Q8,Team=="Team 6"),size=1,color="#D55E00")+ geom_point(data=subset(Q8,Team=="Team 6"),size=2,color="#D55E00")+ theme(panel.background = element_rect(fill="#F0EDED",color="#F0EDED")) + ggtitle("Monthly 'Likely to recommend Instruction Partners' Average") +xlab("Date") + ylab("'Likely to recommend Instruction Partners' Average") 
```



### Team 7
```{r echo=FALSE, warning=FALSE}
# plot the montly mean for Team 7
ggplot(Q8, aes(month, avg)) + geom_line(data=subset(Q8,Team=="Team 7"),size=1,color="#CC79A7")+ geom_point(data=subset(Q8,Team=="Team 7"),size=2,color="#CC79A7")+ theme(panel.background = element_rect(fill="#F0EDED",color="#F0EDED")) + ggtitle("Monthly 'Likely to recommend Instruction Partners' Average") +xlab("Date") + ylab("'Likely to recommend Instruction Partners' Average") 
```


### Team 8
```{r echo=FALSE, warning=FALSE, message=FALSE}
# plot the montly mean for Team 8
ggplot(Q8, aes(month, avg)) + geom_line(data=subset(Q8,Team=="Team 8"),size=1,color="#336633")+ geom_point(data=subset(Q8,Team=="Team 8"),size=2,color="#336633")+ theme(panel.background = element_rect(fill="#F0EDED",color="#F0EDED")) + ggtitle("Monthly 'Likely to recommend Instruction Partners' Average") +xlab("Date") + ylab("'Likely to recommend Instruction Partners' Average") 
```


### Team 9
```{r echo=FALSE, warning=FALSE}
# plot the montly mean for Team 9
ggplot(Q8, aes(month, avg)) + geom_line(data=subset(Q8,Team=="Team 9"),size=1) + geom_point(data=subset(Q8,Team=="Team 9"),size=2)+ theme(panel.background = element_rect(fill="#F0EDED",color="#F0EDED")) + ggtitle("Monthly 'Likely to recommend Instruction Partners' Average") +xlab("Date") + ylab("'Likely to recommend Instruction Partners' Average") 
```


## Survey Question Responses {.tabset} 
Overall, there's a high rate of agreement among attendees for each question. Teachers are less likely than administrators to strongly agree with a question. While teachers have higher rates of answers below strongly agree, administrators are more likely to disagree with a question. Most notably, teachers seem less clear about roles and responsibilities, the change we seek, and they feel less equipped after the event. 
<br />

### Clear about change we seek
```{r include=FALSE}
# filter out non-answers, get counts of each answer
Q1 <- filter(data, `Clear about change we seek` != "N/A") %>% group_by(`Submitter Role`, `Clear about change we seek`) %>% summarise(var_counts = n())

# get percentage of each answer for each submitter role
asst_prin <- filter(Q1, `Submitter Role` == "Assistant Principal") 
asst_prin$var_per <- with(asst_prin, var_counts/sum(var_counts))
dist_lead <- filter(Q1, `Submitter Role` == "District Leader / CMO Leader")
dist_lead$var_per <- with(dist_lead, var_counts/sum(var_counts))
inst_coach <- filter(Q1, `Submitter Role` == "Instructional Coach") 
inst_coach$var_per <- with(inst_coach, var_counts/sum(var_counts))
other <- filter(Q1, `Submitter Role` == "Other") 
other$var_per <- with(other, var_counts/sum(var_counts))
principal <- filter(Q1, `Submitter Role` == "Principal") 
principal$var_per <- with(principal, var_counts/sum(var_counts))
super <- filter(Q1, `Submitter Role` == "Superintendent / CMO Executive Director") 
super$var_per <- with(super, var_counts/sum(var_counts))
teacher <- filter(Q1, `Submitter Role` == "Teacher")
teacher$var_per <- with(teacher, var_counts/sum(var_counts))
teach_lead <- filter(Q1, `Submitter Role` == "Teacher Leader") 
teach_lead$var_per <- with(teach_lead, var_counts/sum(var_counts))
Q1 = rbind(asst_prin,dist_lead,inst_coach,other,principal,super,teacher,teach_lead)
Q1
```

```{r echo=FALSE, warning=FALSE}
# get color palette
color_palette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

# reorder answers
new_order1  <-factor(Q1$`Clear about change we seek`, levels=c("Strongly Disagree", "Disagree","Somewhat Disagree", "Neutral","Somewhat Agree","Agree","Strongly Agree"))

# plot results
ggplot(Q1, aes(`Submitter Role`, var_per), ) +   
  geom_bar(aes(fill = new_order1),position = position_dodge2(width = 5, preserve = "single"), stat="identity") + theme(plot.title = element_text(size = 12, face = "bold"), axis.text.x = element_text(angle = 60, hjust = 1),panel.background = element_rect(fill="#F0EDED",color="#F0EDED")) + ggtitle("Clear about change we seek") +xlab("Submitter Roles") + ylab("Percentage") + guides(fill=guide_legend(title="Agreement")) + scale_fill_manual(values=color_palette)
```

### Clear about roles and responsibilities
```{r include=FALSE}
# filter out non-answers, get counts of each answer
Q2 <- filter(data, `Clear about roles and responsibilities` != "N/A") %>% group_by(`Submitter Role`, `Clear about roles and responsibilities`) %>% summarise(var_counts = n())

# get percentage of each answer for each submitter role
asst_prin <- filter(Q2, `Submitter Role` == "Assistant Principal") 
asst_prin$var_per <- with(asst_prin, var_counts/sum(var_counts))
dist_lead <- filter(Q2, `Submitter Role` == "District Leader / CMO Leader")
dist_lead$var_per <- with(dist_lead, var_counts/sum(var_counts))
inst_coach <- filter(Q2, `Submitter Role` == "Instructional Coach") 
inst_coach$var_per <- with(inst_coach, var_counts/sum(var_counts))
other <- filter(Q2, `Submitter Role` == "Other") 
other$var_per <- with(other, var_counts/sum(var_counts))
principal <- filter(Q2, `Submitter Role` == "Principal") 
principal$var_per <- with(principal, var_counts/sum(var_counts))
super <- filter(Q2, `Submitter Role` == "Superintendent / CMO Executive Director") 
super$var_per <- with(super, var_counts/sum(var_counts))
teacher <- filter(Q2, `Submitter Role` == "Teacher") 
teacher$var_per <- with(teacher, var_counts/sum(var_counts))
teach_lead <- filter(Q2, `Submitter Role` == "Teacher Leader") 
teach_lead$var_per <- with(teach_lead, var_counts/sum(var_counts))
Q2 = rbind(asst_prin,dist_lead,inst_coach,other,principal,super,teacher,teach_lead)
Q2
```


```{r echo=FALSE, warning=FALSE}
new_order2  <-factor(Q2$`Clear about roles and responsibilities`, levels=c("Strongly Disagree", "Disagree","Somewhat Disagree", "Neutral","Somewhat Agree","Agree","Strongly Agree"))

ggplot(Q2, aes(`Submitter Role`, var_per), ) +   
  geom_bar(aes(fill = new_order2),position = position_dodge2(width = 5, preserve = "single"), stat="identity") + theme(plot.title = element_text(size = 12, face = "bold"), axis.text.x = element_text(angle = 60, hjust = 1),panel.background = element_rect(fill="#F0EDED",color="#F0EDED")) + ggtitle("Clear about roles and responsibilities") +xlab("Submitter Roles") + ylab("Percentage") + guides(fill=guide_legend(title="Agreement")) + scale_fill_manual(values=color_palette)
```

### Confident plan will achieve goals
```{r include=FALSE}
# filter out non-answers, get counts of each answer
Q3 <- filter(data, `Confident plan will achieve goals` != "N/A") %>% group_by(`Submitter Role`, `Confident plan will achieve goals`) %>% summarise(var_counts = n())

# get percentage of each answer for each submitter role
asst_prin <- filter(Q3, `Submitter Role` == "Assistant Principal") 
asst_prin$var_per <- with(asst_prin, var_counts/sum(var_counts))
dist_lead <- filter(Q3, `Submitter Role` == "District Leader / CMO Leader")
dist_lead$var_per <- with(dist_lead, var_counts/sum(var_counts))
inst_coach <- filter(Q3, `Submitter Role` == "Instructional Coach") 
inst_coach$var_per <- with(inst_coach, var_counts/sum(var_counts))
other <- filter(Q3, `Submitter Role` == "Other") 
other$var_per <- with(other, var_counts/sum(var_counts))
principal <- filter(Q3, `Submitter Role` == "Principal") 
principal$var_per <- with(principal, var_counts/sum(var_counts))
super <- filter(Q3, `Submitter Role` == "Superintendent / CMO Executive Director") 
super$var_per <- with(super, var_counts/sum(var_counts))
teacher <- filter(Q3, `Submitter Role` == "Teacher") 
teacher$var_per <- with(teacher, var_counts/sum(var_counts))
teach_lead <- filter(Q3, `Submitter Role` == "Teacher Leader") 
teach_lead$var_per <- with(teach_lead, var_counts/sum(var_counts))
Q3 = rbind(asst_prin,dist_lead,inst_coach,other,principal,super,teacher,teach_lead)
Q3
```


```{r echo=FALSE, warning=FALSE}
new_order3  <-factor(Q3$`Confident plan will achieve goals`, levels=c("Strongly Disagree", "Disagree","Somewhat Disagree", "Neutral","Somewhat Agree","Agree","Strongly Agree"))

ggplot(Q3, aes(`Submitter Role`, var_per), ) +   
  geom_bar(aes(fill = new_order3),position = position_dodge2(width = 5, preserve = "single"), stat="identity") + theme(plot.title = element_text(size = 12, face = "bold"), axis.text.x = element_text(angle = 60, hjust = 1),panel.background = element_rect(fill="#F0EDED",color="#F0EDED")) + ggtitle("Confident plan will achieve goals") +xlab("Submitter Roles") + ylab("Percentage") + guides(fill=guide_legend(title="Agreement")) + scale_fill_manual(values=color_palette)
```

### Feel more equipped
```{r include=FALSE}
# filter out non-answers, get counts of each answer
Q4 <- filter(data, `Feel more equipped` != "N/A") %>% group_by(`Submitter Role`, `Feel more equipped`) %>% summarise(var_counts = n())

# get percentage of each answer for each submitter role
asst_prin <- filter(Q4, `Submitter Role` == "Assistant Principal") 
asst_prin$var_per <- with(asst_prin, var_counts/sum(var_counts))
dist_lead <- filter(Q4, `Submitter Role` == "District Leader / CMO Leader")
dist_lead$var_per <- with(dist_lead, var_counts/sum(var_counts))
inst_coach <- filter(Q4, `Submitter Role` == "Instructional Coach") 
inst_coach$var_per <- with(inst_coach, var_counts/sum(var_counts))
other <- filter(Q4, `Submitter Role` == "Other") 
other$var_per <- with(other, var_counts/sum(var_counts))
principal <- filter(Q4, `Submitter Role` == "Principal") 
principal$var_per <- with(principal, var_counts/sum(var_counts))
super <- filter(Q4, `Submitter Role` == "Superintendent / CMO Executive Director") 
super$var_per <- with(super, var_counts/sum(var_counts))
teacher <- filter(Q4, `Submitter Role` == "Teacher") 
teacher$var_per <- with(teacher, var_counts/sum(var_counts))
teach_lead <- filter(Q4, `Submitter Role` == "Teacher Leader") 
teach_lead$var_per <- with(teach_lead, var_counts/sum(var_counts))
Q4 = rbind(asst_prin,dist_lead,inst_coach,other,principal,super,teacher,teach_lead)
Q4
```


```{r echo=FALSE, warning=FALSE}
new_order4  <-factor(Q4$`Feel more equipped`, levels=c("Strongly Disagree", "Disagree","Somewhat Disagree", "Neutral","Somewhat Agree","Agree","Strongly Agree"))

ggplot(Q4, aes(`Submitter Role`, var_per), ) +   
  geom_bar(aes(fill = new_order4),position = position_dodge2(width = 5, preserve = "single"), stat="identity") + theme(plot.title = element_text(size = 12, face = "bold"), axis.text.x = element_text(angle = 60, hjust = 1),panel.background = element_rect(fill="#F0EDED",color="#F0EDED")) + ggtitle("Feel more equipped") +xlab("Submitter Roles") + ylab("Percentage") + guides(fill=guide_legend(title="Agreement")) + scale_fill_manual(values=color_palette)
```

### Equipped and supported
```{r include=FALSE}
# filter out non-answers, get counts of each answer
Q5 <- filter(data, `Equipped and supported` != "N/A") %>% group_by(`Submitter Role`, `Equipped and supported`) %>% summarise(var_counts = n())

# get percentage of each answer for each submitter role
asst_prin <- filter(Q5, `Submitter Role` == "Assistant Principal") 
asst_prin$var_per <- with(asst_prin, var_counts/sum(var_counts))
dist_lead <- filter(Q5, `Submitter Role` == "District Leader / CMO Leader")
dist_lead$var_per <- with(dist_lead, var_counts/sum(var_counts))
inst_coach <- filter(Q5, `Submitter Role` == "Instructional Coach") 
inst_coach$var_per <- with(inst_coach, var_counts/sum(var_counts))
other <- filter(Q5, `Submitter Role` == "Other") 
other$var_per <- with(other, var_counts/sum(var_counts))
principal <- filter(Q5, `Submitter Role` == "Principal") 
principal$var_per <- with(principal, var_counts/sum(var_counts))
super <- filter(Q5, `Submitter Role` == "Superintendent / CMO Executive Director") 
super$var_per <- with(super, var_counts/sum(var_counts))
teacher <- filter(Q5, `Submitter Role` == "Teacher") 
teacher$var_per <- with(teacher, var_counts/sum(var_counts))
teach_lead <- filter(Q5, `Submitter Role` == "Teacher Leader") 
teach_lead$var_per <- with(teach_lead, var_counts/sum(var_counts))
Q5 = rbind(asst_prin,dist_lead,inst_coach,other,principal,super,teacher,teach_lead)
Q5
```


```{r echo=FALSE, warning=FALSE}
new_order5  <-factor(Q5$`Equipped and supported`, levels=c("Strongly Disagree", "Disagree","Somewhat Disagree", "Neutral","Somewhat Agree","Agree","Strongly Agree"))

ggplot(Q5, aes(`Submitter Role`, var_per), ) +   
  geom_bar(aes(fill = new_order5),position = position_dodge2(width = 5, preserve = "single"), stat="identity") + theme(plot.title = element_text(size = 12, face = "bold"), axis.text.x = element_text(angle = 60, hjust = 1),panel.background = element_rect(fill="#F0EDED",color="#F0EDED")) + ggtitle("Equipped and supported") +xlab("Submitter Roles") + ylab("Percentage") + guides(fill=guide_legend(title="Agreement")) + scale_fill_manual(values=color_palette)
```

### Understand state of instruction
```{r include=FALSE}
# filter out non-answers, get counts of each answer
Q6 <- filter(data, `Understand state of instruction` != "N/A") %>% group_by(`Submitter Role`, `Understand state of instruction`) %>% summarise(var_counts = n())

# get percentage of each answer for each submitter role
asst_prin <- filter(Q6, `Submitter Role` == "Assistant Principal") 
asst_prin$var_per <- with(asst_prin, var_counts/sum(var_counts))
dist_lead <- filter(Q6, `Submitter Role` == "District Leader / CMO Leader")
dist_lead$var_per <- with(dist_lead, var_counts/sum(var_counts))
inst_coach <- filter(Q6, `Submitter Role` == "Instructional Coach") 
inst_coach$var_per <- with(inst_coach, var_counts/sum(var_counts))
other <- filter(Q6, `Submitter Role` == "Other") 
other$var_per <- with(other, var_counts/sum(var_counts))
principal <- filter(Q6, `Submitter Role` == "Principal") 
principal$var_per <- with(principal, var_counts/sum(var_counts))
super <- filter(Q6, `Submitter Role` == "Superintendent / CMO Executive Director") 
super$var_per <- with(super, var_counts/sum(var_counts))
teacher <- filter(Q6, `Submitter Role` == "Teacher") 
teacher$var_per <- with(teacher, var_counts/sum(var_counts))
teach_lead <- filter(Q6, `Submitter Role` == "Teacher Leader") 
teach_lead$var_per <- with(teach_lead, var_counts/sum(var_counts))
Q6 = rbind(asst_prin,dist_lead,inst_coach,other,principal,super,teacher,teach_lead)
Q6
```


```{r echo=FALSE, warning=FALSE}
new_order6  <-factor(Q6$`Understand state of instruction`, levels=c("Strongly Disagree", "Disagree","Somewhat Disagree", "Neutral","Somewhat Agree","Agree","Strongly Agree"))

ggplot(Q6, aes(`Submitter Role`, var_per), ) +   
  geom_bar(aes(fill = new_order6),position = position_dodge2(width = 5, preserve = "single"), stat="identity") + theme(plot.title = element_text(size = 12, face = "bold"), axis.text.x = element_text(angle = 60, hjust = 1),panel.background = element_rect(fill="#F0EDED",color="#F0EDED")) + ggtitle("Understand state of instruction") +xlab("Submitter Roles") + ylab("Percentage") + guides(fill=guide_legend(title="Agreement")) + scale_fill_manual(values=color_palette)
```

### Valuable use of my time
```{r include=FALSE}
# filter out non-answers, get counts of each answer
Q7 <- filter(data, `Valuable use of my time:` != "N/A") %>% group_by(`Submitter Role`, `Valuable use of my time:`) %>% summarise(var_counts = n())

# get percentage of each answer for each submitter role
asst_prin <- filter(Q7, `Submitter Role` == "Assistant Principal") 
asst_prin$var_per <- with(asst_prin, var_counts/sum(var_counts))
dist_lead <- filter(Q7, `Submitter Role` == "District Leader / CMO Leader")
dist_lead$var_per <- with(dist_lead, var_counts/sum(var_counts))
inst_coach <- filter(Q7, `Submitter Role` == "Instructional Coach") 
inst_coach$var_per <- with(inst_coach, var_counts/sum(var_counts))
other <- filter(Q7, `Submitter Role` == "Other") 
other$var_per <- with(other, var_counts/sum(var_counts))
principal <- filter(Q7, `Submitter Role` == "Principal") 
principal$var_per <- with(principal, var_counts/sum(var_counts))
super <- filter(Q7, `Submitter Role` == "Superintendent / CMO Executive Director") 
super$var_per <- with(super, var_counts/sum(var_counts))
teacher <- filter(Q7, `Submitter Role` == "Teacher") 
teacher$var_per <- with(teacher, var_counts/sum(var_counts))
teach_lead <- filter(Q7, `Submitter Role` == "Teacher Leader") 
teach_lead$var_per <- with(teach_lead, var_counts/sum(var_counts))
Q7 = rbind(asst_prin,dist_lead,inst_coach,other,principal,super,teacher,teach_lead)
Q7
```


```{r echo=FALSE, warning=FALSE}
new_order7  <-factor(Q7$`Valuable use of my time:`, levels=c("Strongly Disagree", "Disagree","Somewhat Disagree", "Neutral","Somewhat Agree","Agree","Strongly Agree"))

ggplot(Q7, aes(`Submitter Role`, var_per), ) +   
  geom_bar(aes(fill = new_order7),position = position_dodge2(width = 5, preserve = "single"), stat="identity") + theme(plot.title = element_text(size = 12, face = "bold"), axis.text.x = element_text(angle = 60, hjust = 1),panel.background = element_rect(fill="#F0EDED",color="#F0EDED")) + ggtitle("Valuable use of my time") +xlab("Submitter Roles") + ylab("Percentage") + guides(fill=guide_legend(title="Agreement")) + scale_fill_manual(values=color_palette)
```

